% chktex-file 46
%!TeX spellcheck = en-US,it-IT
\RequirePackage{silence} % :-\
\WarningFilter{scrreprt}{Usage of package `titlesec'}
\WarningFilter{titlesec}{Non standard sectioning command detected}
\documentclass[ twoside,openright,titlepage,numbers=noenddot,%1headlines,
 headinclude,footinclude,cleardoublepage=empty,abstract=on,
 BCOR=5mm,paper=a4,fontsize=11pt
]{scrreprt}
%\usepackage{subfigure}
\input{classicthesis-config}
\usepackage{setspace}
\usepackage{verbatim}
\usepackage{amsthm}
\usepackage{todonotes}
\usepackage{wrapfig}
\usepackage{listings}
\usepackage{relsize}
\usepackage{sidecap}
\usepackage{float}
\usepackage[binary-units=true]{siunitx}
\DeclareMathOperator{\tg}{tg}
\theoremstyle{plain}
\newtheorem*{teorema}{Theorem}
\addbibresource{Bibliography.bib}
\DefineBibliographyStrings{english}{phdthesis = {thesis}}
\newcommand\CC{C\nolinebreak[4]\hspace{-.05em}\raisebox{.4ex}{\relsize{-3}{\textbf{++}}}}
\newcommand{\me}{\mathrm{e}}
%\renewcommand{\floatpagefraction}{.8}%
\begin{document}
\frenchspacing
\raggedbottom
\selectlanguage{english}
\pagestyle{plain}

% Frontmatter
\include{FrontBackmatter/Titlepage}
\cleardoublepage\include{FrontBackmatter/Abstract}
\cleardoublepage\include{FrontBackmatter/Contents}

% Mainmatter
\pagestyle{scrheadings}
\chapter{Introduction}
In every day work, high energy physics scientists have to deal with a lot of
data (the \textit{big data}), the effort required to manage and process
this amount of data is a large data is a important and extensive part of a
physicist's work.
The latest developments in the field of machine learning showed that the
usage of deep neural networks can help facing signal background discrimination
problems. The usage of these techniques can speed up the research field of high
energy physics in various ways. They can compare multiple theories at the same
tame (New Physics) against the standard model. Taking as example the CMS
experiment, the actual trigger system are built upon physicists hypothesis,
unexpected events are almost certain lost. These techniques could help solve
these problems. The greatest obstacle to the usage of these methods is the
needed effort of computational resources. These algorithms are slow to train
and bring new technical challenges when it comes to making predictions.

The aim of this thesis is to show that the smart usage of computational
resources with new promising paradigms such as the clustering computing
and GPU architectures can help reduce the time required in these computations.


\part{Background}\label{pt:Background}
\include{Chapters/Chapter01}
\include{Chapters/Chapter02}
%\ctparttext{}
\part{Results}\label{pt:results}
\include{Chapters/Chapter03}

\chapter{Conclusion}
In this thesis work new computational paradigms have been explored. The results
with cluster architecture seems promising. They show that this technique has a
good capability to scale as the number of nodes and computational resources
increases. This characteristic can be exploit for develop large scale system.

Results with GPUs show that them can compete with cluster computing but seems
less encouraging than expected. This can be related with a number of factors such
as, for example, the kind of problem, the implementation or the hyperparameters choice.

Nevertheless, the results are promising, clustering and GPUs are definitely good
ways to improve performance of deep neural networks for solve a discrimination signal background problem.

% Backmatter
\appendix
\cleardoublepage\include{FrontBackmatter/Bibliography}
\end{document}
